Placeholder for article 3

### 2025-01-08 analysis/paper/paper.qmd
Fig-caps, updated word and Legion corrected commit with previous commit stashed.

```{r}
#| label: fig-solutrean-boxplots

@@

```{r}
#| label:  fig-proto-boxplots

@@

```{r}
#| label: fig-gravettian-boxplots

@@

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

```{r}
#| label: fig-solutrean-boxplots
#| fig-cap: Boxplots Gravettian.

@@

```{r}
#| label:  fig-proto-boxplots
#| fig-cap: Boxplots Proto-Solutrean

@@

```{r}
#| label: fig-gravettian-boxplots
#| fig-cap: Boxplots Solutrean

@@
